Budgeted Reinforcement Learning\\in Continuous State Space

### 2020-10-19 paper/poster/poster.tex
Update webpage style

\documentclass[a0paper,portrait,fontscale=0.355, margin=2cm]{baposter}

@@

% Other packages
\usepackage{tabularx}
\def\tabularxcolumn#1{m{#1}}
\def\imagetop#1{\vtop{\null\hbox{#1}}}
\usepackage{adjustbox}
\usepackage{subfig}
\usepackage{floatrow} % sidecapfloat
\usepackage{setspace}
\usepackage{xspace}
\usepackage{noReferences}
\usepackage{caption}
\usepackage{tikz}
\usepackage[customcolors]{hf-tikz}
%\usepackage{subcaption}
\usepackage{epsf}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{dsfont}
\usepackage{enumitem}
\usepackage{float}
\usepackage{cases}
\usepackage{verbatim}
\usepackage{array}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{multirow}
\usepackage{listings}
%\usepackage[authoryear]{natbib}
\usepackage{authblk}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{eqparbox}
\usepackage{xcolor}
\usepackage[backend=biber, citestyle=authoryear, maxcitenames=2, maxbibnames=2]{biblatex}
\usepackage{lipsum}
\usepackage{svg}
\usepackage{cleveref}

@@

\input{style}
\input{../mathdef}

@@

%\background{ % Set the background to an image (background.pdf)
%\begin{tikzpicture}[remember picture,overlay]
%\draw (current page.north west)+(-2em,2em) node[anchor=north west]
%{\includegraphics[height=1.1\textheight]{background.png}};
%\end{tikzpicture}
%}
\begin{poster}{
grid=false,
borderColor=bordercol, % Border color of content boxes
headerColorOne=headercol1, % Background color for the header in the content boxes (left side)
headerColorTwo=headercol2, % Background color for the header in the content boxes (right side)
headerFontColor=headerfontcol, % Text color for the header text in the content boxes
boxColorOne=boxcolor, % Background color for the content in the content boxes
headershape=roundedright, % Specify the rounded corner in the content box headers
%headerfont=\Large\sf\bf, % Font modifiers for the text in the content box headers
headerfont=\Large\bf\textsc, %Sans Serif
textborder=rectangle,
background=none,
headerborder=open, % Change to closed for a line under the content box headers
boxshade=plain,
textfont={\setlength{\parindent}{0.0em}\sffamily},
headerheight={0.05\textheight},
eyecatcher=true
%columns=5
}
%
%----------------------------------------------------------------------------------------
%	Title and authors
%----------------------------------------------------------------------------------------
%
{
\includegraphics[width=18em]{./img/companies}
}
{
Budgeted Reinforcement Learning in Continuous State Space
}
{
Nicolas Carrara, Edouard Leurent, Romain Laroche, \\Tanguy Urvoy, Odalric-Ambrym Maillard, Olivier Pietquin
\vspace{-3\baselineskip}
}
{
\includegraphics[width=14em]{./img/inria_sc}
}

@@

\begin{itemize}[nolistsep]
    \item[\incarrow] \hlr{Single scalar reward} to represent \hlr{multiple} \hlr{contradictory} aspects (e.g. complete task and avoid collisions)
    \item[\incarrow] \hlr{No control over the spread} of the performance distribution\\

\end{itemize}

\textbf{Constrained MDP} $(\cS, \cA, P, R_r, R_c, \gamma)$
\begin{itemize}[nolistsep]
    \item $[$\cite{BEUTLER1985236,Altman95constrainedmarkov}$]$
    \item Introduce a \hlb{cost signal} $R_c$
    \item Constrained objective
\begin{equation*}
\begin{array}{lcr}
 \displaystyle \max_{\pi\in\cM(\cA)^\cS} \expectedvalue[G_r^\pi | s_0=s] & \text{\hlb{ s.t. }} & \expectedvalue[G_c^\pi | s_0=s] \leq \beta
\end{array}
\end{equation*}
\item[\incarrow] The cost budget $\beta$ \hlr{cannot be changed} after training\\
\end{itemize}

\textbf{Budgeted MDP}

\begin{itemize}[nolistsep]
    \item $[$\cite{Boutilier_Lu:uai16}$]$
    \item We seek \hlg{one general policy} $\pi(s,\beta)$ that solves every CMDP for any $\beta$
    \item[\incarrow] Can only be solved for \hlr{finite} $\cS$ and \hlr{known} $P, R_r, R_c$.
\end{itemize}
}

@@

The Bellman Expectation equations% [\cite{Bellman}]
are preserved, and the Bellman Expectation Operator $\cT^\pi$ is a \hlg{$\gamma$-contraction}.
}

%----------------------------------------------------------------------------------------
%	Budgeted Optimality
%----------------------------------------------------------------------------------------
\headerbox{Budgeted Optimality}{name=bopt,column=0,span=1,below=setting}{
\begin{definition*}In that order, we want to:
\begin{enumerate}
    \item[(i)] \hlb{Respect the budget $\beta$}: 
    \begin{equation*}
    \Pi_a(\os) \eqdef \{\pi\in\Pi: V_c^\pi(s, \beta) \leq \beta\}
    \end{equation*}
    \item[(ii)] \hlg{Maximise the rewards}:
    \begin{equation*}
        V_r^*(\os) \eqdef {\max}_{\pi\in\Pi_a(\os)}  V_r^\pi(\os) \qquad\quad \Pi_r(\os) \eqdef \argmax_{\pi\in\Pi_a(\os)}  V_r^\pi(\os)
    \end{equation*}
    \item[(iii)] \hlr{Minimise the costs}: 
    \begin{equation*}
        V_c^*(\os) \eqdef {\min}_{\pi\in\Pi_r(\os)}  V_c^\pi(\os), \qquad\quad \Pi^*(\os) \eqdef \argmin_{\pi\in\Pi_r(\os)}  V_c^\pi(\os)
    \end{equation*}
\end{enumerate}

@@

Despite those theoretical limitations, we observed \hlg{empirical convergence} in our experiments

\bookboxx{
\begin{theorem*}[Contractivity on smooth $Q$-functions]
\label{rmk:contractivity-smooth}
\hlg{$\cT$ is a contraction when restricted} to the subset $\cL_\gamma$ of $Q$-functions such that "$Q_r$ is \hlg{$L$-Lipschitz} with respect to $Q_c$", with $L<\frac{1}{\gamma}-1$.
\end{theorem*}
}
}

@@

\begin{center}
\includegraphics[width=0.8\linewidth]{../source/img/pi.pdf}    
\end{center}
\vspace*{-1em}
\bookboxx{
\begin{proposition*}[Hull policy]
\label{prop:bftq_pi_hull}
$\pi_\text{greedy}$ in \eqref{eq:pi_greedy} can be \hlg{computed explicitly}, as a mixture of two points that lie on the convex hull of $Q$.
\end{proposition*}
}

@@

\begin{center}
\resizebox{.7\textwidth}{!}{%
\input{../source/architecture.tex}
}    
\end{center}

@@

%----------------------------------------------------------------------------------------
%	Acknowledgements
%----------------------------------------------------------------------------------------
\headerbox{Acknowledgements}{name=ack,column=0,span=1,below=bopt}{
This work has been supported by CPER Nord-Pas de Calais/FEDER DATA Advanced data science and technologies 2015-2020, the French Ministry of Higher Education and Research, INRIA, and the French Agence Nationale de la Recherche (ANR).
}

%----------------------------------------------------------------------------------------
%	References
%----------------------------------------------------------------------------------------
\headerbox{References}{name=refs,column=0,span=1,below=ack, above=bottom}{
    {
    \AtNextBibliography{\footnotesize}
    \setlength{\bibitemsep}{3pt}
    \printbibliography[heading=none]
    }
}

>>>>

\documentclass[paperwidth=36in,paperheight=48in,portrait,fontscale=0.355, margin=2cm]{baposter}

@@

% Other packages
\usepackage{tabularx}
\def\tabularxcolumn#1{m{#1}}
\def\imagetop#1{\vtop{\null\hbox{#1}}}
\usepackage{adjustbox}
\usepackage{subfig}
\usepackage{floatrow} % sidecapfloat
\usepackage{setspace}
\usepackage{xspace}
\usepackage{noReferences}
\usepackage{caption}
\usepackage{tikz}
\usepackage[customcolors]{hf-tikz}
%\usepackage{subcaption}
\usepackage{epsf}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{dsfont}
\usepackage{enumitem}
\usepackage{float}
\usepackage{cases}
\usepackage{verbatim}
\usepackage{array}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{multirow}
\usepackage{listings}
%\usepackage[authoryear]{natbib}
\usepackage{authblk}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{eqparbox}
\usepackage{xcolor}
\usepackage[backend=biber, citestyle=authoryear, maxcitenames=2, maxbibnames=2]{biblatex}
\usepackage{lipsum}
\usepackage{svg}
\usepackage{cleveref}
\usepackage{pifont}

@@

\input{style}
\input{../mathdef}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{property}{Property}
\newtheorem{assumption}{Assumption}
\newtheorem{conjecture}{Conjecture}
\newtheorem*{definition*}{Definition}
\newtheorem*{theorem*}{Theorem}
\newtheorem*{proposition*}{Proposition}
\newtheorem*{remark*}{Remark}

@@

%\background{ % Set the background to an image (background.pdf)
%\begin{tikzpicture}[remember picture,overlay]
%\draw (current page.north west)+(-2em,2em) node[anchor=north west]
%{\includegraphics[height=1.1\textheight]{background.png}};
%\end{tikzpicture}
%}
\begin{poster}{
grid=false,
borderColor=bordercol, % Border color of content boxes
headerColorOne=headercol1, % Background color for the header in the content boxes (left side)
headerColorTwo=headercol2, % Background color for the header in the content boxes (right side)
headerFontColor=headerfontcol, % Text color for the header text in the content boxes
boxColorOne=boxcolor, % Background color for the content in the content boxes
headershape=roundedright, % Specify the rounded corner in the content box headers
%headerfont=\Large\sf\bf, % Font modifiers for the text in the content box headers
headerfont=\Large\bf\textsc, %Sans Serif
textborder=rectangle,
background=none,
headerborder=open, % Change to closed for a line under the content box headers
boxshade=plain,
textfont={\setlength{\parindent}{0.0em}\sffamily},
headerheight={0.05\textheight},
eyecatcher=true
%columns=5
}
%
%----------------------------------------------------------------------------------------
%	Title and authors
%----------------------------------------------------------------------------------------
%
{
\includegraphics[width=18em]{./img/companies}
}
{
Budgeted Reinforcement Learning in Continuous State Space
}
{
Nicolas Carrara$^*$, Edouard Leurent$^*$, Romain Laroche, \\Tanguy Urvoy, Odalric-Ambrym Maillard, Olivier Pietquin
\vspace{-3\baselineskip}
}
{
\includegraphics[width=14em]{./img/inria_sc}
}

@@

    \hlr{Single scalar} reward for \hlb{multiple contradictory} aspects 
    \begin{center}
    	\includegraphics[trim={0 1.7cm 0 3cm}, clip, width=0.9\linewidth]{img/pareto}
    \end{center}

\textbf{Constrained MDP} $(\cS, \cA, P, R_r, $\hlb{$R_c$}$, \gamma, $\hlb{$\beta$}$)$
\begin{itemize}[]
    \item $[$\cite{BEUTLER1985236,Altman95constrainedmarkov}$]$
    \item Introduce a cost signal $R_c$ and constrained objective
\begin{equation*}
\begin{array}{lcr}
 \displaystyle \max_{\pi\in\cM(\cA)^\cS} \expectedvalue[G_r^\pi | s_0=s] & \text{\hlb{ s.t. }} & \expectedvalue[G_c^\pi | s_0=s] \leq \beta
\end{array}
\end{equation*}
\item[\incarrow] The cost budget $\beta$ \hlr{cannot be changed} after training\\
\end{itemize}

\textbf{Budgeted MDP} $(\cS, \cA, P, R_r, {R_c}, \gamma, \hleb{\cB})$

\begin{itemize}[]
	\item $[$\cite{Boutilier_Lu:uai16}$]$
    \item We seek \hlg{one general policy} $\pi(s,\beta)$ that solves every CMDP for any $\beta\in\cB$
    \item[\incarrow] Can only be solved for \hlr{finite} $\cS$ and \hlr{known} $P, R_r, R_c$.
\end{itemize}
}

@@

The Bellman Expectation equations are \hlg{preserved}, and the Bellman Expectation Operator $\cT^\pi$ is a \hlg{$\gamma$-contraction}.
}

%----------------------------------------------------------------------------------------
%	Budgeted Optimality
%----------------------------------------------------------------------------------------
\headerbox{Budgeted Optimality}{name=bopt,column=0,span=1,below=setting}{
\begin{definition*}In that order, we want to:
\begin{enumerate}
    \item[(i)] \hlb{Respect the budget $\beta$}: 
    \begin{equation*}
    \Pi_a(\os) \eqdef \{\pi\in\Pi: V_c^\pi(s, \beta) \leq \beta\}
    \end{equation*}
    \item[(ii)] \hlg{Maximise the rewards}:
    \begin{equation*}
        V_r^*(\os) \eqdef {\max}_{\pi\in\Pi_a(\os)}  V_r^\pi(\os), \quad \Pi_r(\os) \eqdef \argmax_{\pi\in\Pi_a(\os)}  V_r^\pi(\os)
    \end{equation*}
    \item[(iii)] \hlr{Minimise the costs}: 
    \begin{equation*}
        V_c^*(\os) \eqdef {\min}_{\pi\in\Pi_r(\os)}  V_c^\pi(\os), \quad \Pi^*(\os) \eqdef \argmin_{\pi\in\Pi_r(\os)}  V_c^\pi(\os)
    \end{equation*}
\end{enumerate}

@@

\begin{itemize}[nolistsep]
	\item[\hlr{\xmark}] We \hlr{cannot guarantee} the convergence of $\cT^n(Q_0)$ to $Q^*$.
\end{itemize}

\bookboxx{
\begin{theorem*}[Contractivity on smooth $Q$-functions]
\label{rmk:contractivity-smooth}
\hlg{$\cT$ is a contraction when restricted} to the subset $\cL_\gamma$ of $Q$-functions such that "$Q_r$ is \hlg{$L$-Lipschitz} with respect to $Q_c$", with $L<\frac{1}{\gamma}-1$.
\end{theorem*}
}
\begin{itemize}[nolistsep]
	\item[\hlg{\checkmark}] We \hlg{guarantee} convergence under some (strong) assumptions.
	\item[\hlg{\checkmark}] We \hlg{observe} empirical convergence.
\end{itemize}
}

@@

\begin{center}
\includegraphics[width=0.76\linewidth]{../source/img/pi.pdf}    
\end{center}
\vspace*{-1em}
\bookboxx{
\begin{proposition*}[Hull policy]
\label{prop:bftq_pi_hull}
$\pi_\text{greedy}$ in \eqref{eq:pi_greedy} can be \hlg{computed explicitly}, as a mixture of two points that lie on the convex hull of $Q$.
\end{proposition*}
}

@@

\begin{center}
\resizebox{.65\textwidth}{!}{%
\input{../source/architecture.tex}
}    
\end{center}

@@

%----------------------------------------------------------------------------------------
%	Acknowledgements
%----------------------------------------------------------------------------------------
\headerbox{Acknowledgements}{name=ack,column=0,span=1,below=bopt, above=bottom}{
This work has been supported by CPER Nord-Pas de Calais/FEDER DATA Advanced data science and technologies 2015-2020, the French Ministry of Higher Education and Research, INRIA, and the French Agence Nationale de la Recherche (ANR).
}

%----------------------------------------------------------------------------------------
%	References
%----------------------------------------------------------------------------------------
%\headerbox{References}{name=refs,column=0,span=1,below=ack, above=bottom}{
%    {
%    \AtNextBibliography{\footnotesize}
%    \setlength{\bibitemsep}{3pt}
%    \printbibliography[heading=none]
%    }
%}

### 2020-10-19 paper/talk/edouard/main.tex
Minor update
Recall CRL graph when introducing BRL
Update webpage style

Reinforcement learning relies on a \alert{single reward function $R$}
\begin{itemize}[<+->]
	\item[\green \checkmark] A convenient formulation, but;
	\item[\red \xmark] $R$ is not always easy to design. 
\end{itemize}

\begin{alertblock}{Conflicting Objectives}
Complex tasks require multiple \alert{contradictory} aspects. Typically:

\begin{center}
	\Large {\green Task completion} \quad vs \quad {\red Safety}
\end{center}
\end{alertblock}
\begin{flushright}
	For example...
\end{flushright}
\end{frame}

@@

\color{black}
For a fixed reward function $R$,
\begin{itemize}
	\item[\incarrow] $\pi^*$ is only guaranteed to lie on a \alert{Pareto-optimal} curve \alert{$\Pi^*$}
	\item[\incarrow] no control over the $\frac{\green \text{Task Completion}}{\red \text{Safety}}$ trade-off
\end{itemize}
\end{frame}

@@

\begin{frame}{We want to learn $\Pi^*$ rather than $\pi^*_\beta$}
\centering
\includegraphics[width=0.9\textwidth]{img/pareto5}
\end{frame}

@@

>>>>

Reinforcement learning relies on a \alert{single reward function $R$}
\begin{itemize}
	\pause\item[\green \checkmark] A convenient formulation, but;
	\pause\item[\red \xmark] $R$ is not always easy to design. 
\end{itemize}
\pause
\begin{alertblock}{Conflicting Objectives}
Complex tasks require multiple \alert{contradictory} aspects. Typically:

\begin{center}
	\Large {\green Task completion} \quad vs \quad {\red Safety}
\end{center}
\end{alertblock}
\pause
\begin{flushright}
	For example...
\end{flushright}
\end{frame}

@@

\color{black}
For a fixed reward function $R$,
\begin{itemize}
	\item[\incarrow] no control over the $\frac{\green \text{Task Completion}}{\red \text{Safety}}$ trade-off
	\item[\incarrow] $\pi^*$ is only guaranteed to lie on a \alert{Pareto-optimal} curve \alert{$\Pi^*$}\end{itemize}
\end{frame}

@@

\begin{frame}{We want to learn $\Pi^*$ rather than $\pi^*_\beta$}
\centering
\includegraphics<1>[width=0.9\textwidth]{img/pareto4}%
\includegraphics<2>[width=0.9\textwidth]{img/pareto5}
\end{frame}

@@

\begin{frame}
\centering \LARGE Thank You!
\end{frame}
